UMAP reveals cryptic population structure and phenotype heterogeneity in large genomic cohorts

### 2019-06-18 ms/main.tex
Add some stuff on PCs and variation

\begin{figure*}
    \centering
    \begin{subfigure}{0.95\textwidth}
    \includegraphics[width=0.95\textwidth]{images/montage_1KGP_umap_convergence_resize.jpeg}
    \end{subfigure}
    \caption{UMAP applied to the first few hundred principal components of the 1KGP data. As more components are added, the figure begins to resemble that of UMAP carried out on the full genotype dataset.}
    \label{fig:supp_montage_1kgp_converge}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}{0.95\textwidth}
    \includegraphics[width=0.95\textwidth]{images/1KGP_UMAP_PCS100_PCE3450_NC2_NN15_MD05_201944185843.jpeg}
    \end{subfigure}
    \caption{UMAP applied the last 3350 principal components of the 1KGP.}
    \label{fig:supp_1kgp_3350}
\end{figure*}

@@

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}{0.95\textwidth}
    \includegraphics[width=0.95\textwidth]{images/montage_1KGP_umap_convergence_resize.jpeg}
    \end{subfigure}
    \caption{UMAP applied to the first few hundred principal components of the 1KGP data with the amount of variance explained in parentheses. As more components are added, the figure begins to resemble that of UMAP carried out on the full genotype dataset.}
    \label{fig:supp_montage_1kgp_converge}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}{0.95\textwidth}
    \includegraphics[width=0.95\textwidth]{images/1KGP_UMAP_PCS100_PCE3450_NC2_NN15_MD05_201944185843.jpeg}
    \end{subfigure}
    \caption{UMAP applied the last 3350 principal components of the 1KGP, which explain 78.7\% of the variation.}
    \label{fig:supp_1kgp_3350}
\end{figure*}

@@

\clearpage
\begin{table}[htb!]
\centering
 \begin{tabular}{||c c||} 
 \hline
 Number of PCs & Variance explained  \\ [0.5ex] 
 \hline\hline
 2 & 13.6\% \\
\hline
3 & 14.7\% \\
\hline
4 & 15.5\% \\
\hline
5 & 15.7\% \\
\hline
6 & 15.8\% \\
\hline
7 & 15.9\% \\
\hline
8 & 16.0\% \\
\hline
9 & 16.1\% \\
\hline
10 & 16.2\% \\
\hline
11 & 16.2\% \\
\hline
12 & 16.3\% \\
\hline
13 & 16.4\% \\
\hline
14 & 16.5\% \\
\hline
15 & 16.5\% \\
\hline
30 & 17.5\% \\
\hline
50 & 18.6\% \\
\hline
100 & 21.3\% \\
\hline
200 & 26.4\% \\
\hline
300 & 31.1\% \\
\hline
400 & 35.5\% \\
\hline
500 & 39.7\% \\
\hline
600 & 43.7\% \\
\hline
700 & 47.4\% \\
\hline
800 & 50.8\% \\
\hline
900 & 54.0\% \\
\hline
1000 & 57.0\% \\
\hline
1100 & 60.0\% \\
\hline
1200 & 62.8\% \\
\hline
1300 & 65.4\% \\
\hline
1400 & 68.0\% \\
\hline
1500 & 70.5\% \\
\hline
1600 & 73.0\% \\
\hline
1700 & 75.3\% \\
\hline
1800 & 77.5\% \\
\hline
1900 & 79.7\% \\
\hline
2000 & 81.8\% \\
\hline
2100 & 83.8\% \\
\hline
2200 & 85.8\% \\
\hline
2300 & 87.6\% \\
\hline
2400 & 89.4\% \\
\hline
2500 & 91.1\% \\
\hline
2600 & 92.7\% \\
\hline
2700 & 94.2\% \\
\hline
2800 & 95.3\% \\
\hline
2900 & 96.3\% \\
\hline
3000 & 97.1\% \\
\hline
3100 & 97.8\% \\
\hline
3200 & 98.5\% \\
\hline
3300 & 99.2\% \\
\hline
3400 & 99.7\% \\[1ex] 
 \hline
 \end{tabular}
 \caption{Variance explained in the 1KGP data by the number of principal components used.}
 \label{table:1KGP_var_exp}
\end{table}
